{ \sffamily \LARGE Electronic supplementary material}\\{\bf \sffamily \LARGE Evolution of reciprocity with limited payoff memory

### 2023-11-05 paper/main.tex
daggers and removes spaces from abstract

\documentclass[11pt]{article}
\usepackage{times}
\usepackage{amsmath,amsthm,amssymb,setspace,enumitem,epsfig,titlesec,verbatim,color,array,eurosym,multirow}
\usepackage[sort&compress,comma,round,numbers]{natbib}
\usepackage[footnotesize,bf]{caption}
\usepackage[margin=2.5cm, includefoot, footskip=30pt]{geometry}
\usepackage{standalone}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage[all]{hypcap}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{blkarray}
\usepackage[ruled,vlined]{algorithm2e}
\smallskip % Erlaubt kleine Abstaende zwischen Paragraphen, falls es dem Seitenlayout hilft
\renewcommand{\baselinestretch}{1.3}
\newcommand{\R}{\mathbb{R}}

@@

\title{\bf  \sffamily \Large Evolution of reciprocity %among individuals\\ 
with limited payoff memory\\}
\date{}
\author{\parbox[c]{16cm}{\centering \onehalfspacing 
Nikoleta E. Glynatsi$^1$,  Alex McAvoy$^{2,3}$, Christian Hilbe$^1$\\ \quad \\
$^{\rm 1}$Max Planck Research Group on the Dynamics of Social Behavior,\\ Max Planck Institute for Evolutionary Biology, Pl\"{o}n, Germany \\
$^{\rm 2}$School of Data Science and Society, University of North Carolina at Chapel Hill,\\ Chapel Hill, NC 27599 \\
$^{\rm 3}$Department of Mathematics, University of North Carolina at Chapel Hill,\\ Chapel Hill, NC 27599}}

>>>>

\documentclass[11pt]{article}
\usepackage{times}
\usepackage{amsmath,amsthm,amssymb,setspace,enumitem,epsfig,titlesec,verbatim,color,array,eurosym,multirow}
\usepackage[sort&compress,comma,round,numbers]{natbib}
\usepackage[footnotesize,bf]{caption}
\usepackage[margin=2.5cm, includefoot, footskip=30pt]{geometry}
\usepackage{standalone}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage[all]{hypcap}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{blkarray}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{lineno}
\linenumbers
\smallskip % Erlaubt kleine Abstaende zwischen Paragraphen, falls es dem Seitenlayout hilft
\renewcommand{\baselinestretch}{1.3}
\newcommand{\R}{\mathbb{R}}

@@

\title{\bf  \sffamily \Large Evolution of reciprocity %among individuals\\ 
with limited payoff memory\\}
\date{}
\author{\parbox[c]{16cm}{\centering \onehalfspacing 
Nikoleta E. Glynatsi$^1$,  Alex McAvoy$^{2,3, \dagger}$, Christian Hilbe$^{1, \dagger}$\\ \quad \\
$^{\rm 1}$Max Planck Research Group on the Dynamics of Social Behavior,\\ Max Planck Institute for Evolutionary Biology, Pl\"{o}n, Germany \\
$^{\rm 2}$School of Data Science and Society, University of North Carolina at Chapel Hill,\\ Chapel Hill, NC 27599 \\
$^{\rm 3}$Department of Mathematics, University of North Carolina at Chapel Hill,\\ Chapel Hill, NC 27599 \\
$^{\rm \dagger}$ A.M. and C.H. contributed equally to this work.}}
